Modal type theory based on the intuitionistic epistemic logic

### 2018-01-25 article.tex
added

    \begin{prooftree}
      \AxiomC{$\Gamma \vdash \vec{M} : {\bf K} \vec{A}$}
      \AxiomC{$\vec{x} : \vec{A} \vdash M : B$}
      \RightLabel{$\text{let}_{{\bf K}}$}
      \BinaryInfC{$\Gamma \vdash {\bf let \: pure \:} \vec{x} = \vec{M} {\: \bf in \: } M : {\bf K} B$}
    \end{prooftree}
  \end{tabular}
  \end{minipage}%

@@

  7) $({\bf let \:\: pure} \:\: \vec{x} = \vec{M} \:\: {\bf in} \:\: M) [y := P] = {\bf let \:\: pure} \:\: \vec{x} = (\vec{M} [y := P]) \:\: {\bf in} \:\: M$.
  \end{defin}

@@

  Now we will prove standard lemmas for contexts in type systems\footnote{We will not prove cases with
  $\to$-constructor, they are proved standardly in the same lemmas for simply typed lambda calculus, for
  example see \cite{Neder}\cite{Morten}\cite{Girard}. We will consider only modal cases}:

@@

  By $K_I$ $\Gamma \vdash {\bf pure \:L} M : {\bf K}(A[B := C])$.
\end{proof}

@@

@@

By default we will consider an arbitrary closed functor on some cartersian closed category, which is the special case of an applicative functor.

We identify terminal objects. So $\mathcal{K}(\mathds{1}) = \mathds{1}$ and $\eta_{\mathds{1}} = id_{\mathds{1}}$ since $\mathcal{K}$ is an endofunctor.

@@

  i) Let $\Gamma \vdash M : A$ and $M \twoheadrightarrow_{\beta} N$, then $[\![\Gamma \vdash M : A]\!] = [\![\Gamma \vdash N : A]\!]$;

  ii) Let $\Gamma \vdash M : A$ and $M \twoheadrightarrow_{\eta} N$, then $[\![\Gamma \vdash M : A]\!] = [\![\Gamma \vdash N : A]\!]$;
\end{lemma}

>>>>

    \begin{prooftree}
      \AxiomC{$\Gamma \vdash \vec{M} : {\bf K} \vec{A}$}
      \AxiomC{$\vec{x} : \vec{A} \vdash N : B$}
      \RightLabel{$\text{let}_{{\bf K}}$}
      \BinaryInfC{$\Gamma \vdash {\bf let \: pure \:} \vec{x} = \vec{M} {\: \bf in \: } N : {\bf K} B$}
    \end{prooftree}
  \end{tabular}
  \end{minipage}%

@@

  7) $({\bf let \: pure \:}\vec{x} = \vec{M} {\: \bf in \:} N) [y := P] = {\bf let \: pure \:} \vec{x} = (\vec{M} [y := P]) {\: \bf in \:} M$.
  \end{defin}

@@

  Now we will prove standard lemmas for contexts in type systems\footnote{We will not prove cases with
  $\to$-constructor, they are proved standardly in the same lemmas for simply typed lambda calculus, for
  example see \cite{Neder} \cite{Morten} \cite{Girard}. We will consider only modal cases}:

@@

  By $K_I$ $\Gamma \vdash {\bf pure \:} M : {\bf K}(A[B := C])$.
\end{proof}

@@

  Normal form in call-by-name $\lambda_{{\bf K}}$ has the subformula property.

\begin{proof}
  By induction on the structure of term. Case with ${\bf let \: pure\:} \vec{x} = \vec{M} {\: \bf in \:} N$ was considered by Kakutani \cite{ModalK} \cite{ModalK1}.
  Similary, if ${\bf pure \:} M$ is a normal form, so $M$ is a normal form too by hypothesis.
\end{proof}

@@

@@

  Let $\Gamma \vdash M : A$ and $M \twoheadrightarrow_{\beta \eta} N$, then $[\![\Gamma \vdash M : A]\!] = [\![\Gamma \vdash N : A]\!]$;
\end{lemma}
